%%%%%%%%%%%%% You can ignore this stuff
\documentclass[bsc]{abdnthesis}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{csquotes}
\usepackage{svg}
\usepackage{pdfpages}
\usepackage{array}
\usepackage{tabularx}

\usepackage[style=apa, backend=biber]{biblatex}
\DefineBibliographyStrings{english}{%
  bibliography = {References},
}

\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{black}{#1}}%
}

\addbibresource{refs.bib}

% This creates hyperlinks and moves the contents links to the page number for clarity
\usepackage[linktocpage=true,hidelinks]{hyperref}	

\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}
\def\sectionautorefname{Section}
\def\chapterautorefname{Chapter}

%%%%%%%%%%%%%%%%% Space for your own packages here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Uncomment for blank lines between paragraphs rather than
% indents
\usepackage[parfill]{parskip}

\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}
% \usepackage{geometry}
\usepackage{longtable}

\graphicspath{/figures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{A Web-based Multi-criteria Bicycle Route Planning Application}
\author{Jake Bailey}
\upnumber{2002753}

\projecttype{Engineering Project}
\school{School of Computing}

%%%% In the final submission of a thesis, this should only be the year
%%%% of submission.  However, it is useful to use \date{\today} for drafts so that
%%%% they don't get mixed up.
    
\date{2024}

%% It is useful to split the document up as chapters and include
%% them.  LaTeX will sort out all the numbering and cross-referencing
%% for you --- if you run it enough times!

\begin{document}

%%%% Create the title page and standard declaration.

\maketitle
\makedeclaration

%%%% Then the abstract and acknowledgements

\begin{abstract}
    Whether to commute or to exercise, cyclists regularly use route planning applications to plan for their journeys. There are many pre-existing applications to allow cyclists to do this; however, most of these have a limited range of customisable criteria used within the routing algorithm.

    This dissertation investigates how the current solutions consider user-customisable criteria in routing algorithms and will provide an open-source prototype system. The proposed system will consider pre-existing data, such as weather and hazard data, whilst catering for custom criteria chosen by the user and location of accommodation for long-distance routes.
\end{abstract}

\begin{acknowledgements}
  I would like to thank Dr. Rich Boakes for his immense support as my project supervisor and personal tutor throughout my degree. His support has been critical to my success and he is someone I have viewed as a role model since I started at Portsmouth. I would also like to thank Dr. Valentin Adamescu for the guidance he provided when developing the database for the artefact and for the support throughout my database modules. Dr. Gail Ollis has also been a great source of feedback during the writing and development of this project and I am grateful for her support.

  I would also like to thank my family and friends for their support throughout my degree. With special mention to Joe, Jack and my partner Tiff. I greatly appreciate the support you have given me, making my time at Portsmouth enjoyable and memorable.
\end{acknowledgements}

%% please indicate whether you are happy for other students to
%% view your project in the future
\section*{Consent to Share}
I consent for this project to be archived by the University Library and potentially used as an example project for future students.


%%%% These are macros ( each macro is defined by \newcommand )
%%%% These macros make cross-referencing easier, building on the
%%%% already very useful \autoref{ref}.  You tweak them or build your own.

%% \autorefp{ref}
%% Like \autoref, but adds the page number
%% e.g. Section 3.2.4 (p345)
\newcommand{\autorefp}[1]{\autoref{#1} (p\pageref*{#1})}

%% \autorefnp{ref}
%% Like \autoref, but adds both the section name and page number
% e.g. Section 3.2.4 "blah blah" (p345)
\newcommand{\autorefnp}[1]{\autoref{#1} ``\nameref{#1}'', (p\pageref*{#1})}

%% \see{ref}
%% Handy shorthand for inserting a hyperlinked xref.
%%   e.g. (see Section 3.2.4, p134)
%%        (see Figure 5.1, p23)
%%        (see Table 4.7, p999)
\newcommand{\see}[1]{\hyperref[#1]{(see \autoref*{#1}, ``\nameref{#1}'', p\pageref*{#1})}}

%% \seenamed{ref}
%% Handy shorthand for inserting a hyperlinked xref that also includes
%% the name of the section being referred to.
%% (see Section 3.2.4 "blah blah", p134)
%% (see Figure 5.1 "blah blah blah!", p23)
%% (see Table 4.7 "blah blah blah blah blah blah", p999)
\newcommand{\seenamed}[1]{\hyperref[#1]{(see \autoref*{#1} ``\nameref*{#1}'', p.\pageref*{#1})}}

%% \bq Block Quotations.
\newcommand{\bq}[2][]{\singlespacing \begin{quote} 
\begin{small} ``\textit{#2}'' \end{small} #1 \end{quote} \doublespacing}

%% \qq{quotation}
%% Shortcut for doing inline quotations (with 6699 quotation marks around italic text)
%% e.g. \qq{To be, or not to be}
\newcommand{\qq}[1]{{\enquote{\textit{#1}}}}



%%%% It should have a table of contents, but delete the other two as
%%%% necessary.

\tableofcontents
\listoftables
\listoffigures

\include{02-introduction}
\include{03-litreview}
\include{04-methodology}
\include{05-project_management}
\include{06-requirements}
\include{07-design}
\include{08-implementation}
\include{09-testing}
\include{10-evaluation}
\include{11-reflection_and_conclusion}

%%%%%%%%%%%%%% REFERENCES SECTION
\newpage
\phantomsection
\addcontentsline{toc}{chapter}{References}
% In order to try and get a consistent format I copy and paste the INSPIRE bibtex code into my bibtex file.
\printbibliography

%%%%%%%%%%%% Include your appendices here

\appendix
\include{12-appendix-a}

\include{13-appendix-b}

% \include{14-appendix-c}

% \include{15-appendix-d}

% \include{16-appendix-e}

% \include{17-appendix-f}

% \include{18-appendix-g}

\end{document}
